Vagueness, Noise, and Communication

### 2014-10-07 paper/04_discussion.tex
Small corrections to discussion section.

We have introduced a new variant of the replicator mutator dynamics
that implements specifically stochastic noise in the form of
confusability of similar states. The probabilities of confusing nearby
similar states is easily implemented in behavioral strategies, but can
also be translated into a mutation matrix for pure strategies. This
allows, in principle, several conceptual interpretations of the \rdd,
on which we will briefly enlarge below in
Section~\ref{sec:model-interpretation}.

@@

\paragraph{Generalized reinforcement.}
\citet{OConnor2013:The-Evolution-o} introduces a generalization of
Herrnstein reinforcement learning for sim-max games and showed that
this not only leads to vague signaling patterns, but can speed-up
evolution of efficient signaling strategies, especially in games with
many states.

@@

That this is conceptually odd shows even more clearly in a case where
the state space is intuitively unbounded, as for instance for the
property ``tall''. If the usual interpretation of a ``tall man'' peaks
at around, say, 195cm then when meeting a giant of $n$ meters senders
would, according to the quantal response approach, be ever more
inclined to describe the giant indifferently as either ``tall'' or
``short'' the larger $n$ gets. This is because, as the distance from
the prototype increases for larger $n$, the difference between the
expected utilities of saying ``short'' or ``tall'' will converge to
zero. Whence that the quantal response approach would predict that
senders would grow indifferent between choice of antonyms as $n$
grows, which seems weird.

>>>>

We have introduced a new variant of the replicator mutator dynamics
that implements specifically stochastic noise in the form of
confusability of similar states. The probabilities of confusing nearby
similar states is easily implemented in behavioral strategies, but can
also be translated into a mutation matrix for pure strategies. This
allows, in principle, several conceptual interpretations of the \rdd,
on which we will briefly elaborate below in
Section~\ref{sec:model-interpretation}.

@@

\paragraph{Generalized reinforcement.}
% Repeated below...
%\citet{OConnor2013:The-Evolution-o} introduced a generalization of
%Herrnstein reinforcement learning for sim-max games and showed that
%this not only leads to vague signaling patterns, but can speed-up
%evolution of efficient signaling strategies, especially in games with
%many states.

@@

That this is conceptually odd shows even more clearly in a case where
the state space is intuitively unbounded, as for instance for the
property ``tall''. If the usual interpretation of a ``tall man'' peaks
at around, say, 195cm then when meeting a giant of $n$ meters senders
would, according to the quantal response approach, be ever more
inclined to describe the giant indifferently as either ``tall'' or
``short'' the larger $n$ gets. This is because, as the distance from
the prototype increases for larger $n$, the difference between the
expected utilities of saying ``short'' or ``tall'' will converge to
zero. 
%Whence that the quantal response approach would predict that
%senders would grow indifferent between choice of antonyms as $n$
%grows, which seems weird.
